Increasing prevalence of plant-fungal symbiosis across two centuries of environmental change

### 2024-12-31 Manuscript/Reviewer_response_endo_herbarium.tex

\comment{L498: This is a good point as well. Moreover, the uses of eDNA metabarcoding or other sequencing methods to characterise the identity of your Epichloe composition would be very interesting to disscuss at this point. Would you expect a turnover of species (from Epichloe genera), that could impact the performance and potentially something about the dynamics of the plant-symbiotic dynamic?}
\response{lines \ref{}}

\comment{L501: “Second”, I did not see the “First”.}
\response{lines \ref{}}

\comment{Supplementary figures:-Page 1; I don’t know if its journal guidelines, but, should there be a title page, with authors information, affiliations and a title being Appendix to “Increasing prevalence of plant-fungal symbiosis across two centuries of environmental change” ?}
\response{lines \ref{}}

\comment{Fig.A3: Which data were used to produce the simulated datasets? Which model is this from?}
\response{lines \ref{}}

\comment{A4 and A5: Which model, which data? (All plants, all years)?}
\response{lines \ref{}}

\comment{A6; From which models this is from? How probabilities are calculated? What is A and T?}
\response{lines \ref{}}

\comment{A7; From which models; what is the legend for the value means, what is $\tau$?}
\response{lines \ref{}}

\comment{A8;redefine what is liberal vs conservative; what AGPE, AGHY and ELVI means if the Panel B-C-F is from which model. What are the value? (This is an average per year, across 200 years?)}
\response{lines \ref{}}

\comment{A9;A10; Specify models}
\response{lines \ref{}}

\comment{A11; Legend need specifications, the data need to be specified as well.}
\response{lines \ref{}}

\comment{Table A1. Which models, what are the columns names? It is for the full temporal I guess? Need to be specified.}
\response{lines \ref{}}

% ======================================================= %
\end{document}
% ======================================================= %
